---
title: '**Visualisation**: Project'
author: 'Name: Adarsha Mondal | Roll Number: MDS202205'
date: 'Dead Line : 02 Nov 2022'
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(gridExtra)
library(reshape2)
library(ggpubr)
library(knitr)
library(kableExtra)
library(data.table)
```

------------------------------------------------------------------------

## Abstract

## Introduction

A Portuguese banking institution's direct marketing campaigns are covered by the dataset. The marketing campaigns were based on phone conversations. Often, it was necessary to make multiple frequent contacts with the same client in order to determine whether the product (in this case, bank term deposit) would be subscribed ('yes') or not ('no').

Our primary goal is to formulate descriptive statistics visualization with the graphical tools avilable in R language(mainly, **ggplot2**).

## Dataset Information

```{r echo = FALSE}
loaded_data = read.csv(file = "./data/bank_dataset.csv")
setDT(loaded_data)    # convert data.frame into data.table
```

Our data contains `r nrow(loaded_data)` observations and `r length(loaded_data)` attributes, where 11 are categorical and 10 are numerical attributes. The table below contains a portion of the analysed data and names of all the attributes, along with their types and values that they contains.

```{r}
kable(loaded_data[1:6,], caption = "Figure 1: Example of the dataset.", longtable=T, booktabs=T) %>% 
  kable_styling(font_size=7)
```

-   **Bank Client data:**

1.  *age* (numeric)
2.  *job* : type of job (categorical: 'admin.','blue-collar','entrepreneur','housemaid','management','retired','self-employed','services','student','technician','unemployed','unknown')
3.  *marital* : marital status (categorical: 'divorced','married','single','unknown'; note: 'divorced' means divorced or widowed)
4.  *education*: Educational Qualification (categorical: 'basic.4y','basic.6y','basic.9y','high.school','illiterate','professional.course','university.degree','unknown')
5.  *default* : has credit in default? (categorical: 'no','yes','unknown')
6.  *housing* : has housing loan? (categorical: 'no','yes','unknown')
7.  *loan* : has personal loan? (categorical: 'no','yes','unknown')

-   **related with the last contact of the current campaign:**

8.  *contact* : contact communication type (categorical: 'cellular','telephone')
9.  *month* : last contact month of year (categorical: 'jan', 'feb', 'mar', ..., 'nov', 'dec')
10. *day_of_week*: last contact day of the week (categorical: 'mon','tue','wed','thu','fri')
11. *duration*: last contact duration, in seconds (numeric). Important note: this attribute highly affects the output target (e.g., if duration=0 then y='no'). Yet, the duration is not known before a call is performed. Also, after the end of the call y is obviously known. Thus, this input should only be included for benchmark purposes and should be discarded if the intention is to have a realistic predictive model.

-   **Other attributes:**

12. *campaign*: number of contacts performed during this campaign and for this client (numeric, includes last contact)
13. *pdays* : number of days that passed by after the client was last contacted from a previous campaign (numeric; 999 means client was not previously contacted)
14. *previous*: number of contacts performed before this campaign and for this client (numeric)
15. *poutcome*: outcome of the previous marketing campaign (categorical: 'failure','nonexistent','success')

-   **Social and Economic context attributes:**

16. *emp.var.rate* : employment variation rate --- quarterly indicator (numeric)
17. *cons.price.idx*: consumer price index --- monthly indicator (numeric)
18. *cons.conf.idx* : consumer confidence index --- monthly indicator (numeric)
19. *euribor3m* : euribor 3 month rate --- daily indicator (numeric)
20. *nr.employed* : number of employees --- quarterly indicator (numeric)

-   **Output variable (desired target):**

21. *subscribed*: has the client subscribed a term deposit? (binary: 'yes','no')

## Visualization

## Conclusion
